\MakeUppercase{Graph Product Structure for Non-Minor-Closed Classes}

### 2022-03-23 k-planar.tex
Section to subsection
better  qn d-map bound

Since all the product structure theorems presented thus far upper bound the treewidth of $H$,
\cref{qn} immediately implies bounds on the queue number of all graphs in these classes.  An improvement can be made in the cases where $H$ is planar and has treewidth $3$, as follows.
\citet{ABGKP20} proved that every planar graph with treewidth at most $3$ has queue-number at most $5$. Thus the graph $H$ in \cref{1_planar_product} has queue-number at most $5$. \cref{qn,1_planar_product,dMapProduct} then imply:

@@

\begin{cor}
\label{dMapQueue}
Every $d$-map graph has queue-number at most $24 (d+3\floor{d/2}-3) \,  - \ceil{\tfrac{3}{2} (d+3\floor{d/2}-3)}$.
\end{cor}

@@

The following corollary summarizes the results for other graph classes.
\begin{cor}\label{q_cor}
  The following bounds hold for the queue number of any graph from each of the following classes:
  \begin{compactenum}
    \item $k$-planar: $2^{O(k^3)}$
    \item $(g,k)$-planar: $\max\{1,g\}\cdot 2^{O(k^3)}$
    \item $(g,\delta)$-string: $\max\{1,g\}\cdot 2^{O(\delta^3)}$
    \item $1$-planar: $115$
    \item $d$-map: $24 (d+3\floor{d/2}-3) \,  - \ceil{\tfrac{3}{2} (d+3\floor{d/2}-3)}$
    \item $(g,d)$-map: $\max\{1,g\}\cdot 2^{O(d)}$
    \item $k$-NN: $2^{O(k^6)}$
    % \item $(g,d)$-map graph
    % \item
  \end{compactenum}
\end{cor}

@@

\section{Orphaned Theorems}

>>>>

Since all the product structure theorems presented thus far upper bound the treewidth of $H$,
\cref{qn} immediately implies bounds on the queue number of all graphs in these classes.  An improvement can be made in the cases where $H$ is planar and has treewidth $3$, as follows.
\citet{ABGKP20} proved that every planar graph with treewidth at most $3$ has queue-number at most $5$. Thus the graph $H$ in \cref{1_planar_product,dMapProduct} has queue-number at most $5$, which with \cref{qn} implies:

@@

\begin{cor}
\label{dMapQueue}
Every $d$-map graph has queue-number at most 
$15 (d+3\floor{d/2}-3)  + \floor{\tfrac{3}{2}(d+3\floor{d/2}-3)}$.
\note{DW}{I have updated this bound using the better qn bound for planar 3-trees. Note that with $d=3$ we get the original bound of 49.}
\end{cor}

@@

The following corollary summarizes the results for other graph classes.
\begin{cor}\label{q_cor}
  The following bounds hold for the queue number of any graph from each of the following classes:
  \begin{compactenum}
    \item $k$-planar: $2^{O(k^3)}$
    \item $(g,k)$-planar: $\max\{1,g\}\cdot 2^{O(k^3)}$
    \item $(g,\delta)$-string: $\max\{1,g\}\cdot 2^{O(\delta^3)}$
    \item $1$-planar: $115$ \note{DW}{delete?}
    \item $d$-map: $24 (d+3\floor{d/2}-3) \,  - \ceil{\tfrac{3}{2} (d+3\floor{d/2}-3)}$ \note{DW}{delete?}
    \item $(g,d)$-map: $\max\{1,g\}\cdot 2^{O(d)}$
    \item $k$-NN: $2^{O(k^6)}$
    % \item $(g,d)$-map graph
    % \item
  \end{compactenum}
\end{cor}

@@

\subsection{Orphaned Theorems}
